### 2017-02-27 pkg/Pmisc/inst/docs/document.Rmd
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@1655 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

knitr::opts_chunk$set(
  echo=FALSE, prompt=TRUE, comment=NA,
		margins=1, fig.cap=' ',
		fig.width=2.75, fig.height=2.75,  dpi=250, 
		tidy=TRUE, tidy.opts=list(indent=2, width.cutoff=55)
)

@@

mdTable(x=mytable, digits=3,
  caption = 'the table', caption.loc='bottom')

>>>>

knitr::opts_chunk$set(
  echo=FALSE, prompt=TRUE, comment=NA,
		margins=1, fig.cap=' ', fig.pos='ht',
		fig.width=2.75, fig.height=2.75,  dpi=250, 
		tidy=TRUE, tidy.opts=list(indent=2, width.cutoff=55)
)

@@

Pmisc::mdTable(x=mytable, digits=3,
  caption = 'the table', caption.loc='bottom')
